Calculating life expectancy and exploring missingness

### 2016-11-10 Code/1_Explore_Data_v2.Rmd

BlackWhite <- BlackWhite %>% mutate(WBgap = le.birth.white - le.birth.black,
                                    WBgap5 = le.birth.white5 - le.birth.black5,
                                    WBgap9 = le.birth.white9 - le.birth.black9)
```

@@

```{r save_specified_files}
save(dat.clean, dat2, BlackWhite, paired.ids, list.age.decomp.tables, list.cod.decomp.tables,
     list.age.decomp.tables5, list.cod.decomp.tables5, list.age.decomp.tables9, list.cod.decomp.tables9,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```

>>>>

BlackWhite <- BlackWhite %>% mutate(WBgap = le.birth.white - le.birth.black,
                                    WBgap5 = le.birth.white5 - le.birth.black5,
                                    WBgap9 = le.birth.white9 - le.birth.black9)

rm(Black, White)
```

@@

```{r save_specified_files}
save(dat.clean, dat2, BlackWhite, BlackWhiteSmooth, paired.ids, list.age.decomp.tables, list.cod.decomp.tables,
     list.age.decomp.tables5, list.cod.decomp.tables5, list.age.decomp.tables9, list.cod.decomp.tables9,
     list.age.decomp.tables.smoothed, list.cod.decomp.tables.smoothed,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```
